Computing solution space properties by generic programming tensor networks \thanks{\funding{...}}

### 2022-03-21 paper/paper.tex

This appendix covers some technical aspects of this paper, including an open source package and a gist about how to implement this package. If you are only interested in using, please checking our GitHub repository for an efficient and full featured implementation aimed for productively:
\href{https://github.com/Happy-Diode/GraphTensorNetworks.jl}{https://github.com/Happy-Diode/GraphTensorNetworks.jl}.
One can install these packages by opening a Julia REPL, type \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and type, e.g.
\begin{lstlisting}
pkg> add GraphTensorNetworks
\end{lstlisting}
To use it, just open Julia REPL and type

@@

>>>>

This appendix covers some technical aspects of this paper, including an open source package and a gist about how to implement this package. If you are only interested in using, please checking our GitHub repository for an efficient and full featured implementation aimed for productively:
\href{https://github.com/Happy-Diode/GraphTensorNetworks.jl}{https://github.com/Happy-Diode/GraphTensorNetworks.jl}.
One can install these packages by opening a Julia REPL, type \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and type, e.g.
\begin{lstlisting}
pkg> add GraphTensorNetworks
\end{lstlisting}

To use it for solving solution space properties, just open a Julia REPL and type

@@

Here the main function \texttt{solve} takes two inputs, the problem instance of type \texttt{IndependentSet} and the property instance of type \texttt{GraphPolynomial}, while the problem instance also takes two arguments to initialize, one is the graph instance one wants to solve and the key word argument \texttt{optimizer} is for tensor network optimization.

\centering{\includegraphics[width=0.8\textwidth, trim={0cm 1cm 0cm 1cm}, clip]{figures/fig7.pdf}}
